{\bf A Review on Recent Advances in Unsupervised Relation Extraction} \\ \it Term Paper for Recent Advances on Semantics \\ supervised by Prof.Dr.Pinkal

### 2013-07-20 term-paper/paper.tex
Added: USP

\section{PATTY}
\label{ch:unsupervised}

>>>>

In this section we will review the first unsupervised semantic parsing method which proposed by Poon and Domingos ???,
we will first define what is semantic parsing and after describing the method in ??? we show its application for relation extraction.
In the evaluation subsection we will compare this model to its related models and analyze its advantages and disadvantages.

\subsection{Semantic Parsing}
\label{ch:definition}

Semantic parsing is mapping a sentence to its formal meaning represntation ???%cite{PoonDomingos2009}
The aim is to represent a natural language text with first-order logic. One can derive a semantic parse of a sentence
by starting from a lexicon of atomic formulas and combining each fragment to build a composition of 
formulas combined with quantifiers and logical connectives. In ???%cite{PoonDomingos2009} 
 the lexicon will be induced from a raw corpus. It is in contrast to traditional means of semantic parsing with manually
  produced lexicons.

  The main challange in unsupervised semantic parsing is that for a single semantic representation there could be
  several syntactic realizations or even harder, different surface representations. For example, all of the
   sentences below has a same semantic representation:
   \begin{itemize}
     \item Microsoft buys Skype
     \item Microsoft acquires the VoIP company Skype
     \item Skype is acquired by Microsoft Corporation
     \item The Redmond software giant buys Skype
     \item Microsoft’s purchase of Skype,\ldots
   \end{itemize}

   A simple lexicon to represent all of the examples above is:

   $$ BUY(n_1)$$
   $$ \lambda x_2.BUYER(n_1 , x_2) \; \;  \lambda x_3.BOUGHT(n_1 , x_3) $$
   $$ MICROSOFT(n_2) \; \; SKYPE(n_3)$$

   Having a corpus of sentences in natural language, USP %???\cite{domingosPoon}
    will induce such a lexicon and will also extract a formal representation for each sentence. In the next 
    subsection we will review the necessary steps toward this goal.
\subsection{Model Description}
\label{ch:model}

\subsection {Evaluation}
\label{ch:evaluation}
sdgdsg
